\section{Nonfunctional Requirements}
\subsection{Performance Requirements}
AnonChess will not have memory leaks, will use no more than 256 MB of memory and no more than 10\% of the processor 
at any time (these are peak maximums). It will require the latest version of Java 6 SE and an internet connection faster 
than dial-up (56K).
\subsubsection{Computer Requirements}
AnonChess will not allow for more than 1 error in every 100 moves. If it does encounter any error, it will present 
to the user enough details to be helpful without giving away security details.
\subsubsection{Program Stability}
AnonChess will not install any malicious software on any user's machine. It will not perform any malicious actions 
at any time, and will do nothing that is unrelated to executing itself in order to let users play chess.
\subsection{Security Requirements}
\subsubsection{Program Platform}
AnonChess will work on any modern computer capable of running a Java virtual machine, and will thus be operating 
system independent.
\subsubsection{Program Modules}
AnonChess will be built with high cohesion and low coupling in mind, using modules/layers that can interface with 
each other, thus allowing for extensibility and upgrades with minimal time involved.
\subsubsection{Program Usability}
AnonChess will be intuitive to use and will feature adequate instructions for specific implementations of the chess 
game (meaning that it will not describe rules in depth, but will describe specific instructions for how to play 
specifically AnonChess, for instance what the user needs to do to make a move). The game will have no more than a 3 
second lag between user input and response.
